Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-06-11 pdocs/thesis/epj-jcgt.tex
jcgt article - first pdf

% Simo.Nikula@gmail.com
\def\mytitle{Breakable Elastic-plastic Constraint for Rigid Body Simulation}
\def\lut{Lappeenranta University of Technology}
\def\

\documentclass{jcgt}

\setciteauthor{Simo Nikula, Aki Mikkola and Timo Björk}
\setcitetitle{\\mytitle}

% Mark submissions with the date of submission using the following line:
\submitted{\today}

% Once an article is accepted accepted, switch to the following line and comment the preceding one. The editor will supply the argument values.
%\accepted{2014-02-07}{2014-02-07}{2014-02-07}{Editor Name}{3}{1}{1}{1}{2014}
%\seturl{http://jcgt.org/published/0003/01/01/}

@@

\begin{document}
\newcommand{\cbullet}[0]{Bullet Physics}
\title{\\mytitle}

\author
       {SIMO NIKULA {\upshape and} AKI MIKKOLA {\upshape and} TIMO BJÖRK\\\lut
       }

\teaser{
  \includegraphics[width=2in]{figs/demolisher-done.PNG}
  \label{fig:teaser}
  \caption{Adding ductile breakable constraint to popular open source physics engines \cbullet\ and Box2D
allows more realistic simulation of many scenarios.
}
}

@@

\paragraph{Limitations}
Forces are calculated by dividing impulse by timestep and maximum impulse is calculated
by multiplying maximum force by timestep. 
This means that simulation of quick interactions requires small timestep.
This limitation is not introduced by this approach but is build in feature of impulse-based simulation.

Multiaxial stress is not taken into account.

@@

In this work, strain hardening is taken into account by assuming that plastic volume in bending
expands, 
\cite{dowling}.
%\citet[p.~672]{dowling}.
Material that starts to yield first is hardened and as a result of which yielding moves.

The difference between the elastic and plastic section modulus is depicted in Figure \ref{fig:wp}.

@@

\begin {table}
\tbl {Maximum forces and moments for 
rectangular section with width $b$ and height $h$ using constant yield stress $f_y$}{
\begin{tabular}{| c| c|}
\hline
{\bf Direction} & {\bf Maximum value}  \\ \hline
maximum shear force & $0.5\, b\, h f_y$ \\ \hline
maximum normal force & $b\, h\, f_y$  \\ \hline
maximum bending moment in direction of $h$& $0.25\, b\, h^2 \, f_y$  \\ \hline
maximum bending moment in direction of $b$ & $0.25\, b^2\, h\, f_y$  \\ \hline
maximum torque & $ \approx 0.19\, b\, h\, \frac{b\, + h}{2} f_y$  \\ \hline
\end{tabular}}
\label{tab:maxForces} 
\end {table}

@@

\section{Implementation for \cbullet\}

\small
\bibliographystyle{jcgt}
\bibliography{paper}

@@

\hspace{-2mm}\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
Simo Nikula\newline
\href{mailto:Simo.Nikula@gmail.com}{Simo.Nikula@gmail.com}
&
Aki Mikkola\newline
\href{mailto:Aki.Mikkola@lut.fi}{Aki.Mikkola@lut.fi}
&
Timo Björk\newline
\href{mailto:Timo.Bjork@lut.fi}{Timo.Bjork@lut.fi}

\end{tabular}

>>>>

% Simo.Nikula@gmail.com
\def\mytitle{Breakable Elastic-plastic Constraint for Rigid Body Simulation}
\def\lut{Lappeenranta University of Technology}

\documentclass{jcgt}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage[utf8]{inputenc}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\setciteauthor{Simo Nikula, Aki Mikkola and Timo Björk}
\setcitetitle{\mytitle}

% Mark submissions with the date of submission using the following line:
%\submitted{\today}

% Once an article is accepted accepted, switch to the following line and comment the preceding one. The editor will supply the argument values.
\accepted{2014-02-07}{2014-02-07}{2014-02-07}{Editor Name}{3}{1}{1}{1}{2014}
\seturl{http://jcgt.org/published/0003/01/01/}

@@

\begin{document}
\newcommand{\cbullet}[0]{Bullet Physics}
\title{Breakable Elastic-plastic Constraint for\\Rigid Body Simulation}

\author
       {Simo Nikula  Aki Mikkola Timo Björk\\\lut
       }

\teaser{
  \includegraphics[width=5cm]{figs/demolisher-done}
  \label{fig:teaser}
  \caption{Adding ductile breakable constraint to popular open source physics engines \cbullet\ and Box2D allows more realistic simulation of many scenarios.}
}

@@

\paragraph{Limitations}
Forces are calculated by dividing impulse by timestep and maximum impulse is calculated
by multiplying maximum force by timestep. 
This means that simulation of quick interactions requires small timestep.
This limitation is not introduced by this approach but is build in feature of impulse-based simulation.
Bending moment - normal force interactions and multiaxial stress are not taken into account. 
Basically these limitations just state that results from these simulations cannot not be used
for structural analysis.

@@

In this work, strain hardening is taken into account by assuming that plastic volume in bending
expands, 
\cite{dowling}.
%\citet[p.~672]{dowling}.
Material that starts to yield first is hardened and as a result of which yielding moves.
%
The difference between the elastic and plastic section modulus is depicted in Figure \ref{fig:wp}.

@@

\begin {table}
\small
\begin{center}
\begin{tabular}{| c| c|}
\hline
{\bf Direction} & {\bf Maximum value}  \\ \hline
maximum shear force & $0.5\, b\, h f_y$ \\ \hline
maximum normal force & $b\, h\, f_y$  \\ \hline
maximum bending moment in direction of $h$& $0.25\, b\, h^2 \, f_y$  \\ \hline
maximum bending moment in direction of $b$ & $0.25\, b^2\, h\, f_y$  \\ \hline
maximum torque & $ \approx 0.19\, b\, h\, \frac{b\, + h}{2} f_y$  \\ \hline
\end{tabular}
\end{center}
\caption{Maximum forces and moments for 
rectangular section with width $b$ and height $h$ using constant yield stress $f_y$}
\label{tab:maxForces} 
\end {table}

@@

\section{Implementation for \cbullet}

\small
\bibliographystyle{jcgt}
\bibliography{ref}

@@

\hspace{-2mm}\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.3\textwidth}}
Simo Nikula\newline
\href{mailto:Simo.Nikula@gmail.com}{Simo.Nikula@gmail.com}
&
Aki Mikkola\newline
\href{mailto:Aki.Mikkola@lut.fi}{Aki.Mikkola@lut.fi}
&
Timo Björk\newline
\href{mailto:Timo.Bjork@lut.fi}{Timo.Bjork@lut.fi}
\end{tabular}
